pirouette: Quantifying the importance of a tree prior in Bayesian phylogenetics

### 2019-03-18 article.tex
Review ERQ 5, progress https://github.com/richelbilderbeek/pirouette/issues/220

We need to combine these experiments into one set:

@@

We choose again to use sensible defaults for the third (the BEAST2 inference) 
and fourth (measuring the error) steps, as we previously did to answer the 
second research question. To get an idea of a baseline error made by BEAST2, we 
also make use of the twinning option:

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments,
  twinning_params = create_twinning_params()
)
\end{lstlisting}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%
\section{Data Accessibility}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%

>>>>

We need to combine these experiments into one set of experiments:

@@

We choose again to use the default error measurement parameters
as created in listing~\ref{lst:create_error_measure_params}
and combine this with the same twinning parameters 
as used in listing~\ref{lst:create_twinning_params}:

\begin{lstlisting}[language=R, floatplacement=H, frame=single]
pir_params <- create_pir_params(
  alignment_params = alignment_params,
  experiments = experiments,
  error_measure_params = error_measure_params,
  twinning_params = twinning_params
)
\end{lstlisting}

Running the experiment in the usual fashion:

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Data Accessibility}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
